---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "The Analysis of Core PCA drivers for Currency Rates"
subtitle: "Financial Econometric Project"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Jessica Van der Berg"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch Univeristy, South Africa" # First Author's Affiliation
Email1: "20190565\\@sun.ac.za" # First Author's Email address

CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "PCA \\sep Emerging Market \\sep Developing Market" # Use \\sep to separate
JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

Adding additional latex packages:
# header-includes:
    - \usepackage{colortbl} 
    - \usepackage{amsmath}
    - \usepackage{graphicx}
    - \usepackage{adjustbox}
    - \usepackage{caption}
    - \usepackage{float}
    - \usepackage{subfig}
    - \usepackage{subcaption}

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  Using principal component analysis, I identify the core driving factors of emerging and developing market currency rates. I analyse 33 currencies from 1994-03-30 to 2021-10-29. I find that the first principal component is related to commodities, especially oil. The second principal component relates to political instability and the absence of violence/terrorism. The third principal component relates to some Asian factor.  These factors can be used in further studies to make predictions about currency rates and determine whether they are under/overvalued.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(dplyr)
library(readxl)
library("FactoMineR")
library("factoextra")
library("corrplot")
library(gridExtra)
library(grid)
library(ggplot2)
library(lattice)
library(scales)
library(ggpmisc)
library(stats)
library(tseries)

pacman::p_load("tidyverse", "devtools", "rugarch", "forecast", 
               "tbl2xts", "lubridate", "PerformanceAnalytics", "ggthemes", 
               "robustbase")

currency <- readRDS("C:/Users/jesic/OneDrive/Desktop/DATA/currencies.rds")

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}


The foreign exchange market is the largest financial market in the world, and it is extremely liquid. It provides investors with a lot of flexibility, since there are no restrictions on the total amount of money that one individual can use for investing. Furthermore, there is also no regulation of the market, implying that it operates on a 24-7 basis @tana.  However, investing in currency rates have often been overlooked as a potential resource of returns for a variety of reasons.  One reason is that currency rates can be challenging to model. The underlying source of value of a currency rate is elusive @pojar. An economic model for currency valuation often uses fundamental macroeconomic variables, such as real income or national money supply, to estimate the fair value of the currency rate. However, these models are often overly restrictive and account for country-specific macroeconomic variables, making it nearly impossible to replicate the results across currency rates. Therefore, an economic model that works well for a specific currency or period may not necessarily work well for other currencies or periods. There is also the risk of central bank intervention in currency rates which deters investors from investing.  However, profit opportunities in the currency market are available but are subject to a high level of risk and are mostly suitable for specialist @pono. 

Taking these shortcomings and strengths into account, this paper uses principal component analysis to analyse the relationship between currency rates and macroeconomic variables. By examining 33 emerging and developing market currency rates, the paper concludes that shocks to commodity prices, such as an oil price shock, political instability and the Asian economy are all important macroeconomic variables that account for most of the variation in currency rates. 

The paper is structured as follows: Section 2 briefly discusses the data, methodology and some descriptive statistics of the principal component analysis. Section 3 provides an in-depth discussion about the core principal component drivers for currency rates. Section 4 forecasts the three most traded currency rates. Finally, section 5 concludes.



```{r}
currency_spread <- currency %>% spread(Name, Price)

# Removing weekend from dateset 
no_weekend <- currency_spread[which(weekdays(as.Date(currency_spread$date, format = "%m/%d/%Y"))
         %in% c('Monday','Tuesday', 'Wednesday', 'Thursday', 'Friday')), ]

# getting rid of NA data
final <- no_weekend[-c(1:1107),]

# Making data tidy 
try1 <- final %>% gather(Curry, Value, -date) %>% mutate(Curr1 = gsub("_Cncy", "", Curry)) %>% mutate(Currency=gsub("_Inv","",Curr1))

data <- try1[ , c("date", "Currency", "Value", "Curry", "Curr1")]
data <- data[, -c(4,5)]

use_data <- data %>% spread(Currency, Value)
```


```{r}
# Only emerging and developed countries - not frontiers
use <- use_data[,-c(2,4,6,15,23,29,40,42)]

use <- use %>% select(-date)

# By hand 
covmat <- cov(use)
# Em is emerging and DM is devleoped, both with date column. 

res.pca <- PCA(use, graph = FALSE)


eig.val <- get_eigenvalue(res.pca)

# Scree plot 
scree <- fviz_eig(res.pca, addlabels = TRUE, ylim = c(0, 50))

w <- res.pca[["ind"]][["dist"]]
date <- use_data$date
plot_data <- data.frame(date, w)
pc1 <- plot_data %>% ggplot() + 
    geom_line(aes(x = plot_data$date, y = plot_data$w), color ="steelblue") + 
    fmxdat::theme_fmx() +
    labs(y = "", x ="date", title = "First Principal Component", subtitle = "") +
    theme(legend.position = "none") 



```




```{r}
var <- get_pca_var(res.pca)


# Coordinates
obs1 <- head(var$coord)
# Cos2: quality on the factore map
obs2 <- head(var$cos2)
# Contributions to the principal components
obs3 <- head(var$contrib)


graph1 <- fviz_pca_var(res.pca, col.var = "black")

# graph2 <- corrplot(var$cos2, method="color")

graph3 <- fviz_cos2(res.pca, choice = "var", axes = 1:2)


# Contributions of variables to PC1
graph4 <- fviz_contrib(res.pca, choice = "var", axes = 1, top = 10)
# Contributions of variables to PC2
graph5 <- fviz_contrib(res.pca, choice = "var", axes = 2, top = 10)

# Total contribution by Pc1 and PC2
graph6 <- fviz_contrib(res.pca, choice = "var", axes = 1:2, top = 10)


graph7 <- fviz_pca_var(res.pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))



```

# PCA Analysis 

This paper analysis daily currency rates from the 30th of March 1990 till the 29th of October 2021. The currency rates are all relative to USD.  The currency rates were split into emerging and developing markets according to the Morgan Stanley Capital International (MSCI) 2021 annual market classification. Frontier and standalone markets were not considered. Table \ref{cncy} in appendix A displays the countries under consideration. Ultimately, 12 developing markets and 21 Emerging markets were analysed. Figure \ref{data} in appendix A plots the rates of all 33 currencies.

Analysing 41 emerging and developing market currency rates result in very large datasets that need interpretation. Empirical techniques have been developed to decrease the dimensionality of a large dataset. One such empirical technique is principal component analysis (PCA), which is used to reduce the dimensionality of large datasets in an interpretable way while minimizing information loss.  To achieve this, a new uncorrelated variable is created, known as the principal component, which maximizes the variance @jolli. The PCA yields 33 orthogonal principal components. To examine the relative importance of each principal component, I compare the scale of the eigenvalues of the variance-covariance matrix. The results are displayed in the scree plot in figure \ref{scree}.

\begin{figure}[h]
\centering
\includegraphics[scale=0.7]{scree.jpg}
\caption{Scree plot}
\label{scree}
\end{figure}

The scree plot indicates that the first principal component explains 42.9 percent of the variability, the second explains 27.5 percent and the third explains 10.5 percent. Therefore, the first three principal components explain 80.9 percent of the total variation. Figure \ref{pcpc} displays the first principal component. There is a drastic increase around 2008 during the financial crisis. This reflects the sharp appreciation of the USD against most currencies. The US dollar strengthens due to the global \emph{flight to safety} into US Treasury bills as well as the reversal of carry trades @mcc2009. The same pattern can be seen during 2020 when the COVID_19 crisis was in full effect, however, the extent is much smaller. 

\begin{figure}
\centering
\includegraphics[scale=0.9]{pc1.jpg}
\caption{First Principal Component }
\label{pcpc}
\end{figure}

# Identifying Common Drivers 

The principal component is used to analyse the driving forces. By comparing the eigenvalues of the variance-covariance matrix in the previous section, I determined that the first three principal components explain the majority of the total variance of the currency rates.  In this section, I examine the correlation between the first three principal component and the currency rates, as well as provide economic interpretations around the core driving factors that affect currency rates. 

Table \ref{pca1} in appendix B shows the correlation and p-value for the first principal component (PC1). The country that has the highest positive correlation with PC1 is Hungary (HUF), which is a net importer of crude petroleum. Saudi Arabia (SAR) and the United Arab Emirates (AED) are two of the top exporting countries. China (CNY) is the only country with a negative correlation with PC1, with its top import being refined petroleum.  Therefore, one would expect that the oil price is one of the core PCA drivers for currencies.

Oil is an extremely important, non-renewable resource. The demand and price for oil tend to drastically increase with world economic development @li2015. Crude oil is quoted in the U.S dollar, therefore there is a direct relationship between the two. Theoretically, an appreciation in the US dollar should cause a decrease in the price of oil. However, empirical research has found contradicting results, indicating a bi-directional causality relationship between oil and currency rates @beck2020.  Fluctuations in the oil prices are diverse and unique, depending on whether a country is a net importing or net exporting country. For oil-importing countries, @castro found that an oil price shock leads to depreciation of the home currency in the short run, however, the long-run effects are diverse.

For oil-exporting countries, it has been empirically proven that instability in the oil price does not have a significant effect on economic growth. Table \ref{pca1} supports the results of @can2021 who found a much stronger correlation for oil-importing countries. China is a unique case has it is one of the largest importers and exporters of oil. @li2015 found a non-linear causality between the oil price and the RMB exchange rate. This indicates that movement in the price of oil can cause co-movement of RMB with a one-month lag. Since the relationship between the oil price and currency rates are diverse and unique, policymakers should react with caution when examining currency rate pressure.

Table \ref{pca2} in appendix B displays the correlation and the p-value for the second principal component (PC2). The countries that have the highest correlation with PC2 are, amongst others, Singapore (SGD), New Zealand (NZD), Australia (AUD) and Canada (CAD), all developing market economies. The countries with the lowest correlation with PC2 are Turkey (TRY), Egypt (EGP) and Mexico (MXN). This suggest that the PC2 is related to political stability. Countries with a high political stability and absence of violence/terrorism ranking are highly correlated with PC2, whereas countries with a low ranking are often negatively correlated with PC2. 

A country with a high political stability ranking offer much more safe and attractive investment opportunity for foreign investors. This implies that political stability has a significant effect on currency rates. Political unrest, such a serious allegation into government conduct can contribute to the destabilization of an economy, which will weaken currency rates. Changes in currency rates are known as \emph{exchange rate risk} which accounts for uncertainty in movement in the exchange rate between the home and receiver country @higg.

Although the effect of political instability is profound, @levis found that the relationship between political instability in developed countries and foreign direct invest are highly significant in the short run, but not the long run. This would suggest that foreign investors adjust quickly to new developments and that political stability should be considered in conjunction with numerous other relevant factors. 

The correlation and the p-value for the third principal component is represented in Table \ref{pca3} in appendix B. The countries with the largest correlation all appear in Asia and the countries with the lowest correlation are all developed market. This implies that the third principal component is an Asia-specific factor. Over the past few areas, Asian countries have experienced phenomenal growth, which has created profitable opportunities for foreign investors. 

# Forecasting 

Forecasting currency rates is important to many fields such as international business and monetary policy. However, it is challenging to obtain accurate forecasts due to the fluctuations caused by political instability, shocks to commodity prices and economic events. From an investing point of view, an accurate forecast reduces risk related to international investments as well as maximizes returns.  Monetary policy also depends on an accurate forecast of currency rates, as changes in the interest rate can either appreciate or depreciate the home currency. Changes in currency rate affect trade, which affects economic growth. Therefore, an accurate currency forecast can assist authorities to implement effective policies that boost economic growth @shen. In this section, I attempt to forecast the three most traded currencies: the Euro (EU), the Pound sterling (GBP) and the Japanese yen (JPY).  Figure \ref{for} displays the currency rate for the three currencies, all relative to USD.

\begin{figure}
\centering 
\begin{minipage}[t]{8.2cm} 
\centering 
 \includegraphics[width=\linewidth]{for1.jpg} 
 \end{minipage} 
 \hspace{0.1cm} 
 \begin{minipage}[t]{8.2cm} 
 \centering 
 \includegraphics[width=\linewidth]{for2.jpg} 
 \end{minipage}
\caption{The three most traded currencies}
\label{for}
\end{figure}

I employ a 30 period ahead Autoregressive Integrated Moving Average (ARIMA) model to forecast currency rates. @akin found that the ARIMA model performs relatively well when compared to other forecasting methods. Figure \ref{for1} and figure \ref{for2} show the forecasting results for the selected currencies with a 95 per cent upper and lower bound. The forecast results indicate that the USD/GBP rate is forecasted to decrease, implying that the Pound sterling is going to strengthen. However, the actual data shows the opposite effect, the GBP currency rate weakened. 

The forecast results indicate that the USD/EU rate is forecasted to increase slightly, implying that the euro is going to decrease. Actual data support this forecast. The forecast results indicate that the USD/JPY rate is forecasted to decrease slightly, implying that the Pound sterling is going to strengthen. Actual data shows that the currency rate remained relatively stable, making the forecast results mostly accurate. The results should be further investigated to conclude on the forecast accuracy, however, this was out of the scope of this paper. 

\begin{figure}
\centering 
\begin{minipage}[t]{8.2cm} 
\centering 
 \includegraphics[width=\linewidth]{fore1.jpg} 
 \end{minipage} 
 \hspace{0.1cm} 
 \begin{minipage}[t]{8.2cm} 
 \centering 
 \includegraphics[width=\linewidth]{fore2.jpg} 
 \end{minipage}
\caption{Forecasting Results (1)}
\label{for1}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.5]{fore3.jpg}
\caption{Forecasing Results (2)}
\label{for2}
\end{figure}

\newpage
# Conclusion

This paper uses 33 emerging and domestic market currency rates to determine which macroeconomic variables are most important when analysing currency rates.  Since economic models are accompanied with many short comings, such as being overly restrictive, this paper uses a principal component analysis technique to reduce the dimensionality of the datasets in an interpretable way while minimizing information loss. The paper concludes that shocks to commodity prices, such as an oil price shock, political instability and the growth of Asian markets should all be used to build prediction models of sport returns. 

\newpage

# References {-}

<div id="refs"></div>

# Appendix A {-}

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|c|} 
 \hline
 \multicolumn{2}{|c|}{Emerging Market} & \multicolumn{2}{|c|} {Developed Market} \\
 \hline
 Currency & ISO Code & Currency & ISO Code \\
 \hline
  Sol & PEN & Japanese Yen & JPY \\
 Saudi riyal & SAR &  Hong Kong dollar & HKD \\
 New Taiwan dollar & TWD & Canadian dollar & CAD \\
 Czech koruna & CZK & Danish krone & DKK \\
 South Korean won & KRW & Euro & EUR \\
 Renminbi & CNY & Australian dollar & AUD \\
 Indian rupee & INR &  New Zealand dollar & NZD \\
 Brazilian real & BRL & Singapore dollar & SGD \\
 Turkish lira & TRY &  Swedish Krona & SEK  \\
 Russian ruble & RUB & Norwegian krone & NOK \\
 South African rand & ZAR & Isreali Shekel & ILS \\
 Mexican peso & MXN & Pound sterling & GBP \\
 Columbian peso & COP & & \\
 Egyptian pound & EGP & & \\
 Chilean peso & CLP & & \\
 Hungarian forint & HUF & & \\
 Malaysian ringgit & MYR & & \\
 Phillipine peso & PHP & & \\
Thai bath & THB & & \\
United Arab Emirates dirham & AED & & \\
Polish złoty & PLN & & \\
\hline
\end{tabular}
\caption{Description of currencies}
 \label{cncy}
\end{center}
\end{table}

```{r}

## This picture is saved and will be pasted into (just the code for it.)
g <- data %>% ggplot() + 
    geom_line(aes(date, Value, color= Currency)) + 
    fmxdat::theme_fmx() + 
    facet_wrap(~Currency, scales = "free_y") + 
    theme(legend.position = "none") 


```

\begin{figure}
\centering
\includegraphics[scale=0.55]{descriptive.jpg}
\caption{Currency rates of all 33 emerging and developing market countries}
\label{data}
\end{figure}

# Apprendix B {-}

```{r}
# This shows the correlation and p-value. 

res.desc <- dimdesc(res.pca, axes = 1:3, proba = 0.05)
# Description of dimension 1
res1 <- res.desc$Dim.1

# Description of dimension 2
res2 <- res.desc$Dim.2

res3 <- res.desc$Dim.3
```


\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|} 
 \hline
 & Correlation & P-value  \\
 \hline
 HUF & 0.9262878 & 0.000000e+00 \\
 MYR & 0.9114497 & 0.000000e+00 \\
 CLP & 0.9065261 & 0.000000e+00 \\
 PEN & 0.8988561 & 0.000000e+00 \\
 PLN & 0.8780890 & 0.000000e+00 \\
 COP & 0.8751020 & 0.000000e+00 \\
 NOK & 0.8378328 & 0.000000e+00 \\
 SEK & 0.8330755 & 0.000000e+00 \\
 BRL & 0.8263736 & 0.000000e+00 \\
 RUB & 0.7871421 & 0.000000e+00 \\
 ZAR & 0.7857282 & 0.000000e+00 \\
 INR & 0.7411845 & 0.000000e+00 \\
 PHP & 0.7307233 & 0.000000e+00 \\
 MXN & 0.6843628 & 0.000000e+00 \\ 
 TRY & 0.6753067 & 0.000000e+00 \\
 EUR & 0.6577914 & 0.000000e+00 \\
 DKK & 0.6479256 & 0.000000e+00 \\
 KRW & 0.6422958 & 0.000000e+00 \\
 GBP & 0.6259090 & 0.000000e+00 \\
 EGP & 0.6216001 & 0.000000e+00 \\
 AUD & 0.5593268 & 0.000000e+00 \\
 THB & 0.5319724 & 0.000000e+00 \\
 HKD & 0.5177139 & 0.000000e+00 \\
 TWD & 0.4758927 & 0.000000e+00 \\
 CAD & 0.4283742 & 3.557371e-319 \\
 JPY & 0.4241386 & 2.822415e-319 \\
 NZD & 0.3989511 & 3.069525e-273 \\
 ILS & 0.3742421 & 4.183071e-238 \\
 SGD & 0.2588114 & 1.665786e-110 \\
 CZK & 0.2551624 & 2.320584e-107 \\
 AED & 0.2038677 & 2.137731e-68 \\
 SAR & 0.1573449 & 3.994842e-41 \\
 CNY & -0.1710389 & 2.206939e-48 \\
\hline
\end{tabular}
\caption{Correlation and P-value for the first principal component }
 \label{pca1}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|} 
 \hline
 & Correlation & P-value  \\
 \hline
SGD & 0.90321526 & 0.000000e+00 \\
CZK & 0.87653914 & 0.000000e+00 \\
CNY & 0.86382354 & 0.000000e+00 \\
NZD & 0.83337067 & 0.000000e+00 \\
AUD & 0.75831445 & 0.000000e+00 \\
CAD &  0.71356174 & 0.000000e+00 \\
DKK & 0.63254705 & 0.000000e+00 \\
EUR & 0.62951387 & 0.000000e+00 \\
THB &  0.59809540 & 0.000000e+00 \\
JPY  & 0.53230115 & 0.000000e+00 \\
ILS & 0.48051271 & 0.000000e+00 \\
TWD & 0.42403389 & 4.168569e-312 \\
SEK & 0.35444999 & 4.308577e-212 \\
PLN & 0.26203282 & 2.533385e-113 \\
NOK & 0.19878697 & 4.705671e-65 \\
KRW & 0.14350307 & 1.991097e-34 \\
PEN & 0.11407789 & 2.773568e-22 \\
AED & -0.03178834 & 6.993189e-03 \\
MYR & -0.03679994 & 1.792246e-03 \\
HKD & -0.04911994 & 3.056982e-05 \\
PHP & -0.11881763 & 4.754379e-24 \\
HUF &  -0.13573551 & 6.020449e-31 \\
CLP & -0.21440682 & 1.272391e-75 \\
GBP &  -0.27266672 & 6.567991e-123 \\
COP & -0.36995837 & 2.561588e-232 \\
BRL & -0.43981305 & 0.000000e+00 \\
ZAR & -0.55307034 & 0.000000e+00 \\
RUB & -0.58376817 & 0.000000e+00 \\
INR & -0.62851292 & 0.000000e+00 \\
TRY & -0.64001397 & 0.000000e+00 \\
EGP & -0.64775485 & 0.000000e+00 \\
MXN & -0.69994979 & 0.000000e+00 \\
\hline
\end{tabular}
\caption{Correlation and P-value for the second principal component }
 \label{pca2}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|} 
 \hline
 & Correlation & P-value  \\
 \hline
ILS & 0.69659804 & 0.000000e+00 \\
TWD & 0.68427216 & 0.000000e+00 \\
PHP & 0.61977923 & 0.000000e+00 \\
THB & 0.53049506 & 0.000000e+00 \\
HKD & 0.30858474 & 1.310000e-158 \\
KRW & 0.28839441 & 6.692788e-138 \\
PEN &  0.28634486 & 6.840019e-136 \\
SGD & 0.22758825 & 3.214148e-85 \\
MYR & 0.22365740 & 2.722457e-82 \\
COP & 0.17404390 & 4.636722e-50 \\
AED & 0.09417778 & 1.179695e-15 \\
CLP & 0.08433068 & 7.709335e-13 \\
RUB & -0.02629516 & 2.568733e-02 \\
PLN & -0.04475238 & 1.458206e-04 \\
HUF & -0.07070644 & 1.909999e-09 \\
CNY &  -0.08335190 & 1.413117e-12 \\
INF &  -0.09077720 & 1.198224e-14 \\
ZAR & -0.10617861 & 1.681325e-19 \\
NZD & -0.14852069 & 8.807498e-37 \\
TRY & -0.15874418 & 7.742415e-42 \\
EGP & -0.18399169 & 7.806200e-56 \\
AUD & -0.20033914 & 4.582160e-66 \\
SAR & -0.25871186 & 2.032612e-110 \\
EUR & -0.29838703 & 6.100743e-148 \\
DKK &  -0.31163124 & 7.020576e-162 \\
SEK & -0.32101610 & 3.342782e-172 \\
CZK &  -0.34533690 & 1.002528e-200 \\
CAD & -0.44548362 & 0.000000e+00 \\
NOK &  -0.47271370 & 0.000000e+00 \\
GBP &  -0.61500908 & 0.000000e+00 \\
\hline 
\end{tabular}
\caption{Correlation and P-value for the third principal component}
 \label{pca3}
\end{center}
\end{table}
